---
title: "BIS 505 - Lab 1"
author:  "Josemari Feliciano"
date: "Jan-23-2019, 5-6pm"
output: html_notebook
---

## Datasets today:

Partial titanic roster file that is saved in my GitHub account.

Let us check out the raw data via:
https://raw.githubusercontent.com/neonseri/spring2019_yale_bis505/master/lab1/datasets/titanic.csv

I also stored another dataset involving lung function that we will check later:
https://raw.githubusercontent.com/neonseri/spring2019_yale_bis505/master/lab1/datasets/datafev.txt 

## Reading data:  

Before you try `read.table()` or `read.csv()`, open the file to see raw data.  What is the structure of the dataset? Are they separated by white space or comma? Do they have a header or variable name?  

### read.csv()

```{r}
data1 <- read.csv(file=url("https://raw.githubusercontent.com/neonseri/spring2019_yale_bis505/master/lab1/datasets/titanic.csv"))
data1
```

### read.table()

```{r}
data2 <- read.table(file=url("https://raw.githubusercontent.com/neonseri/spring2019_yale_bis505/master/lab1/datasets/titanic.csv"), sep = "," , header = TRUE)

data2 
```


## Exploring the other dataset:

The link is:  https://raw.githubusercontent.com/neonseri/spring2019_yale_bis505/master/lab1/datasets/datafev.txt

```{r}
data3 <- read.table(file=url("https://raw.githubusercontent.com/neonseri/spring2019_yale_bis505/master/lab1/datasets/datafev.txt"), header = TRUE)
data3
```

## Data Frames

Note:  when data are read by read.table() or any of its derivatives, it gets converted to data frame.

Let us explore data frame below:  

```{r}

```

